Preventing runtime errors of Redis at compile time

### 2015-11-17 paper.tex
4.1: Closed type families

Type families have a wide variaty of applications. They can appear inside type
classes\cite{tfclass}\cite{tfsynonym}, or at toplevel. Toplevel type families
can be used to compute over types, they come in open\cite{tfopen} or closed
forms\cite{tfclosed}. We are using \emph{closed type families} since we need
none of the extensibility provided by open type families, and we may need to
overlap instances, like what we do in defining function cases.

@@

Since Haskell has a phase distinction\cite{phasedistinction} between

To link a symbol with a term-level value

What we need is a \emph{singleton}\cite{singletons}, a type
that has only one instance at the term level.

With \emph{kind polymorphism}\cite{promotion}, we have parametric polymorphism
at the kind level.

@@

% \subsection{Model bindings with Type-level Dictionaries}
% \subsection{Bookkeeping with Type families}
% \subsection{Capture effects with Index Monad}
% \paragraph{Type-level literals}

%
% Values have types, but keys don't. In other words, if we treat keys like
% variables, then Redis behaves likes a dynamically and strongly typed language.

% We can only reuse this key as a \emph{set} after it is removed with \mintinline{text}{DEL}
% explicitly.
%
% \begin{minted}{text}
% redis> DEL some-string
% (integer) 1
% redis> SADD some-string bar
% (integer) 1
% \end{minted}

>>>>

Type families have a wide variaty of applications. They can appear inside type
classes\cite{tfclass}\cite{tfsynonym}, or at toplevel. Toplevel type families
can be used to compute over types, they come in two forms: open\cite{tfopen} and
closed \cite{tfclosed}.

We choose \emph{closed type families}, because it allows overlapping instances,
and we need none of the extensibility provided by open type families.
For example, consider both term-level and type-level \mintinline{haskell}{&&}:

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
(&&) :: Bool -> Bool -> Bool
True && True = True
a    && b    = False

type family And (a :: Bool) (b :: Bool) :: Bool where
    And True True = True
    And a    b    = False
\end{minted}

The first instance of \mintinline{haskell}{And} could be subsumed
under the more general instance \mintinline{haskell}{And a b}.
But the closedness allows these instances to be resoluted in order, just like
how cases are resoluted in term-level functions. Also notice that how much
\mintinline{haskell}{And} resembles to it's term-level brother.

@@

% Since Haskell has a phase distinction\cite{phasedistinction} between
%
% To link a symbol with a term-level value
%
% What we need is a \emph{singleton}\cite{singletons}, a type
% that has only one instance at the term level.

% With \emph{kind polymorphism}\cite{promotion}, we have parametric polymorphism
% at the kind level.

@@
